"Physics is like sex: sure, it may give some practical results, but that's not why we do it." ~Richard Feynman
\\\\
Physics is fun, and while 99\% of the things we learn will never be useful in our everyday lives, that doesn't mean we shouldn't learn it. I've tried my best to create a compact physics guide for all skill levels, and a comprehensive hand crafted question bank with full solutions to strengthen your understanding, and hopefully show you some beauty.
\\\\

\section*{What this Resource is NOT}

This book is not...
\begin{itemize}
    \item used for learning a subject. Learn from your teacher, or \sout{better yet} go to many brilliant online resources. I highly recommend:
    \begin{itemize}
        \item Flipping Physics
        \item Doc Schuster
        \item Michel van Biezen
        \item Khan Academy
    \end{itemize}
    \item 100\% Correct. If you spot a mistake, please email \href{mailto:qilin@xue.email}{qilin@xue.email}
    \item A surefire way to get a good mark. This was created by an amateur for his own purposes, so don't go around crying
\end{itemize}
\newpage
\section*{What this Resource IS}
This book is used as...
\begin{itemize}
    \item a quick refresher. Each chapter contains an \emph{Equations} section where the important equations are listed, as well as a \emph{Tricks} section where common question types are outlined, and contains specific problem solving tricks that teachers may not have taught.
    \item a place to learn from complete solutions to problems varying in difficulty. There are many classical problems that are very difficult, but are solvable using elementary techniques.
    \item a place to practice for a test, or more specifically the AP Exam. It contains dozens if not hundreds of multiple choice questions from real unreleased AP exams. (You won't find these anywhere else on the web) So please don't go around sharing it on Reddit because I'll probably get into a lot of trouble.
\end{itemize}